Clause size reduction with all-UIP Learning

### 2020-02-29 paper.tex
adjust plot's color scheme, a small wording change to specifiy how n_attempt and n_success is updated

\paragraph{$\tgap$:}
$\allUip$ can produce significantly smaller clause. However, when it
does not yield a smaller clause, the cost of the additional resolution
steps can hurt the solver's performance. Since resolution cannot
reduce a clause's $\LBD$, the maximum size reduction obtainable from
$\allUip$ is the difference between the 1-UIP clause's size and its
$\LBD$: $\gap(C_1) = |C_1| - \LBD(C_1)$. When $\gap(C_1)$ is small,
applying $\allUip$ is unlikely to be cost effective. Our approach is
to dynamically set a threshold on $\gap(C_1)$, $\tgap$, such that when
$\gap(C_1) < \tgap$ we do not attempt to reduce the clause
(line~\ref{ln:control}). Initially, $\tgap = 0$, and we count the
number of times $\allUip$ is attempted ($\ntries$) and the number of
times it successfully yields a shorter clause ($\nsuc$)
(line~\ref{ln:try} and \ref{ln:suc}). On every restart if the success
rate is greater  than 80\%, we decrease $\tgap$ by one (not allowing it to
become negative), and if it is less than 80\% we increase $\tgap$
by one.

>>>>

\paragraph{$\tgap$:}
$\allUip$ can produce significantly smaller clause. However, when it
does not yield a smaller clause, the cost of the additional resolution
steps can hurt the solver's performance. Since resolution cannot
reduce a clause's $\LBD$, the maximum size reduction obtainable from
$\allUip$ is the difference between the 1-UIP clause's size and its
$\LBD$: $\gap(C_1) = |C_1| - \LBD(C_1)$. When $\gap(C_1)$ is small,
applying $\allUip$ is unlikely to be cost effective. Our approach is
to dynamically set a threshold on $\gap(C_1)$, $\tgap$, such that when
$\gap(C_1) < \tgap$ we do not attempt to reduce the clause
(line~\ref{ln:control}). Initially, $\tgap = 0$, and we count the
number of times $\allUip$ is attempted ($\ntries$) and the number of
times it successfully yields a shorter clause ($\nsuc$)
(line~\ref{ln:try} and \ref{ln:suc}). On every restart if the success
rate since the last restart is greater than 80\%, we decrease $\tgap$ by one (not allowing it to
become negative), and if it is less than 80\% we increase $\tgap$
by one.
